\section{Conclusion}
\noindent
\setlength{\parindent}{0pt}


In this experiment, several fundamental properties of microwave radiation were investigated successfully. 
The measurements demonstrated characteristic wave phenomena such as interference, diffraction, polarization, 
and total reflection. Furthermore, the experiments showed that many principles known from optics can also be 
observed for microwaves.

Different experimental methods were used to determine the wavelength of the emitted microwave radiation. The 
obtained results were consistent and confirmed the reliability of the measurements and the experimental setup.

The investigation of frustrated total reflection demonstrated the existence of evanescent waves and illustrated 
the microwave analogue of the quantum mechanical tunneling effect. In addition, the polarization measurements 
confirmed that the emitted microwave radiation is linearly polarized.

Using Bragg diffraction on a macroscopic crystal structure, the lattice constant of the artificial crystal could 
be determined. Although small deviations occurred due to experimental uncertainties and alignment errors, the 
measured values were in reasonable agreement with the expected dimensions of the structure.

Finally, the experiments with the circular waveguide demonstrated the efficient transmission of microwaves 
through conductive structures and showed the influence of the waveguide geometry on the polarization properties 
of the transmitted radiation.

Overall, the experiment provided a comprehensive overview of important properties of microwave radiation and 
demonstrated several physical effects that are highly relevant in optics, solid state physics, and modern 
communication technologies.


