\section{Properties of a circular waveguid} \label{sec:wellenleiter}

Waveguides are resonators with two open ends, allowing waves to propagate on its interior from one end to the other with minimal loss of energy by 
restricting the transmission of energy to only the direction of the guide. There are three types of waveguides: acoustic waveguides which direct
sound, optical waveguides which direct light, and radiofrequency waveguides which direct electromagnetic waves other than visible or near visible light. \\
In this part of the experiment one of the last type was used to guide microwaves. It is a hollow conductive metal pipe which inner walls are often plated
with a material which reflects signals as much as possible such that the loss is reduced. For high end waveguides silver or gold is often used.
It works by trapping and "bouncing" the waves off its highly conductive inner walls, directing the energy forward. With that there can be two
different propagation modes, one where the electric field is completely perpendicular to the direction the wave is traveling and one where the
magnetic field is completely perpendicular to the travel direction of the wave.\\
To investigate this a transmitter was placed at one, a receiver was placed at the other end of a waveguide. Despite the curvature and lenght of the guide
a clear signal was detected. To verify that the the signal was transmitted through the interior of the pipe and not just on its surface, we closed one
end with a metal cap. Since no signal, besides the background noise could be detected, it is proof to the previous claim.\\
Finally we examined the polarization of the transmitted waves by rotating the receiver. A strong dependence of the measured signal to the rotation
of the receiver was observed, signaling that the wave leaving the waveguide is indeed polarized. The maximum was observed at a rotation angle of
approximately $90^\circ$ relative to the transmitter. This indicates that the polarization direction was altered during propagation through the waveguide.